Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-03-05 ForegroundSimulations/ms.tex
Update acknowledgements
From 475858c (fgsim):
====================

In ms.tex,

(*) Update acknowledgements
Add caption to figure 6
From 0f8f59c (fgsim):
====================

In ms.tex,

(*) Add caption to figure 6

\begin{figure*}[htb]
\centering
\subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_150.0_MHz_subband.eps}}
\subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_150.0_MHz_subband.eps}} \\
\subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_170.0_MHz_subband.eps}}
\subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
\caption{}
\label{fig:eor-fg-ratios}
\end{figure*}

@@

% \acknowledgments

% This work was supported by the U. S. National Science Foundation (NSF) through award AST-1109257.

>>>>

\begin{figure*}[htb]
\centering
\subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_150.0_MHz_subband.eps}}
\subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_150.0_MHz_subband.eps}} \\
\subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_170.0_MHz_subband.eps}}
\subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
\caption{Lower limits on EoR sensitivity, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky. Each panel corresponds to the EoR model and subband indicated. The baseline vector is specified by its length (in m) and orientation (in degrees) at the bottom and top of the $x$-axis respectively. The color scale is logarithmic. Even with worst-case sensitivity, clearly HERA will be able detect EoR drawn from independent models on all baselines for a large fraction of a full 24~hour sky transit cycle.}
\label{fig:eor-fg-ratios}
\end{figure*}

@@

\acknowledgments

We thank Zaki Ali, Adam Beardsley, and Daniel Jacobs for their valuable inputs during the preparation of this manuscript.
